Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-15 paper.tex
minor fix

Automated formal verification has been employed to ensure correctness and reliability of ECPSs, during the last decade, as well as controller synthesis for ECPSs and HSs \textcolor{red}{add citations}.

>>>>

Automated formal verification has been employed to ensure correctness and reliability of ECPSs, during the last decade, as well as controller synthesis~\cite{Nilsson16,Prabhakar17,EsmaeilZadehSoudjani17,Ames17,tabuada2009verification,Hasuo17,Zamani15} for ECPSs and HSs~\cite{Clarke11,Aerts17,Zhang14,Simko14,Sanwal13,Lee13,Li14}.
